---
title: "CodeBook"
author: "Mariona"
date: "20/5/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## DATA

Human Activity Recognition Using Smartphones

Data collected from the accelerometers from the Samsung Galaxy S smartphone: http://archive.ics.uci.edu/ml/datasets/Human+Activity+Recognition+Using+Smartphones

Data:
https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip


## TRANSFORMATIONS

The run_analysis.R is the script to create the tidy data following the 5 steps required as described in the course         project’s definition:

1. Download and unzip data

Download the dataset and unzip in the directory into a folder called UCI HAR Dataset


2. Files

See all the files that contains UCI HA Dataset

```{r}
files
```

3. Assign each data to variables

Create 8 datasets

```{r}
x_train
y_train
subject_train
x_test
y_test
subject_test
features
activityLabels
```

After assign viarables names


4. Merges the training and the test sets to create one data set.

Merge datasets with rbind and the final one with cbind. First obtain 3 datasets:

```{r}
x
y
subject
```

And finally merge in a final dataset, with cbind:

```{r}
finaldataset
```


5. Extracts only the measurements on the mean and standard deviation for each measurement.

Select the measurements on the mean and standard deviation with the function grepl and finally subset in a new dataset called setforMeanandStd


6. Uses descriptive activity names to name the activities in the data set.

Select the activityID in the setforMeanandStd and changed by the activityType that are the names of the activities.

```{r}
setforMeanandStd
```


7. Appropriately labels the data set with descriptive variable names.

Changes the names of the header of the dataset setforMeanandStd.

```{r}
setforMeanandStd
```


8. From the data set in step 4, creates a second, independent tidy data set with the average of each                      variable for each activity and each subject.

Finllay, group the data by subjectID and activiy and calculate the mean for each one.

```{r}
FinalData
```

Save this that in a txt called tidydata.txt with the function write.table()
